Circumnuclear Media and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-02-20 ms.tex
adding sty
Incoporating new figures into text.

\newcommand{\Mdot}{\dot{M}}
\newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
\newcommand{\Mdote}{\dot{M}_{\rm Edd}}
\newcommand{\Mdotb}{\dot{M}_{\rm bondi}}

@@

If heating is provided by Compton heating alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then equation
(\ref{eq:vC}) can be solved for $\tilde{v}_{\rm w}$ to find
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 106 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 76 \eta_{0.02}^{0.29}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align}

@@

The total gas heating rate, $\vwO$, includes contributions from stellar winds, supernovae, pulsars, and SMBH feedback.  The strength of each heating source will depend explicitely on the SMBH mass and the star formation history in the galactic nuclear region, the latter of which will also vary systematically with the galaxy mass and hence with $\Mbh$.

Figure X show the contributions of various heating sources as a function of time $\tau_{\star}$ after a burst of star formation for a black hole of mass $M_{\bullet} = 10^{XX}M_{\odot}$.  These heating rates are calculated using the stellar wind heating $v_{\rm w}^{\star}$ (Fig.~\ref{fig:vwImp}) and mass return parameter $\eta$ (Fig.~\ref{fig:eta}), the latter of which affects the other sources of feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}], [\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$; eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$; eq.~[\ref{eq:vIa}]).  The Ia heating rate also depends on a convolution of the star formation history and the Ia delay-time distribution (eq.~[\ref{eq:DTD}]).  At early times ($\tau_{\star} \lesssim XXX$), stellar wind heating dominates, but at later times Compton heating dominates.   MSP heating is again found to be negligible at all black hole masses.  Epochs of thermally-unstable accretion are shown as a dashed line, indicating that Compton heating becomes important only during the phase of unstable accretion.

From Figure X we conclude that thermally unstable accretion is the norm.  However, a single burst of star formation does not describe the average star formation histories of most galaxies.  Qualitatively, smaller galaxies will on average have more recent star formation, resulting in energetic young stellar winds and supernovae which dominate the energy budget, resulting in a high heating rate of $\vwO \sim 1000 $ km s$^{-1}$.  Massive galaxies, on the other hand, will on average have older stellar populations, with their heating rates dominated by Ia supernovae (on large radial scales) and SMBH feedback.  The average value of $\vwO$ is estimated as a function of SMBH mass for each heating source by calculating its value using the average cosmic star formation histories of \citet{MosterNaab+:2013a}.  Appendix \ref{app:windheat} describes how the average star formation history is used to determine the stellar wind heating $v_{\rm w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).

@@

@@

\begin{figure}
\includegraphics[width=\columnwidth]{eta.pdf}
\caption{\label{fig:eta} Parameter  $\eta$ characterizing stellar mass loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass $\Mbh$, calculated for average star formation histories from \citet{MosterNaab+:2013a} for galaxies with halo masses corresponding to $\Mbh$. }
\end{figure}

@@

Hower, the mass accretion rate is also a sensitive function of the assumed heating rate, such that $\dot{M}\sim\vwO^{-3.8(-2.4)}$ for a core(cusp) galaxies, respectively.  Thus, only a weak positive dependence of $v_{w} \propto M_{\bullet}^{0.25-0.3}$ would be sufficient to explain the trend in X-ray luminosity with BH masses in scenarios where $L_X \propto \dot{M}$, or a somewhat steeper dependence $v_{w} \propto M_{\bullet}^{0.35-0.45}$ if $L_{X} \propto \dot{M}^{2}$.  What could cause this dependence?  Maybe Ia SNa...

@@

One possible solution that the wind mass loss rate $\eta$ increases
with $\Mbh$, as would be expected if low mass SMBH preferentially
hosted younger stellar populations.  Another possible explanation is
that the effective heating rate of the CNM $v_{w}$ decreases
with decreasing SMBH mass.  This could again be due to an older
stellar population, since $v_{w} \propto \eta^{-1/2}$ for heating
sources such as SN Ia and millisecond pulsars.
{\bf AG given our new results on stellar wind heating as a function of
Mbh. It seems like the first statement is indeed true but I suspect
vwO actually increases for low Mbh and that this effect actually dominates.}
%, or it could be due to the fact that Ia occur too infrequently inside
%the stagnation radius for low mass black holes.
%AG-We now think that SNe Ia would become important only at the
%highest values of Mbh.
%AG-Note sure where the best place for this discussion would
%be--here or after presenting the comparisons with Miller et al.

>>>>

\newcommand{\Mdot}{\dot{M}}
\newcommand{\eddr}{\dot{M}/\dot{M}_{\rm Edd}}
\newcommand{\MdotEdd}{\dot{M}_{\rm Edd}}
\newcommand{\Mdotb}{\dot{M}_{\rm bondi}}

@@

If heating is provided by Compton heating alone, i.e. $\tilde{v}_{w} = v_{w}^{C}$, then equation
(\ref{eq:vC}) can be solved for $\tilde{v}_{\rm w}$ to find
\begin{align} v_{w}^{\rm C} \simeq
  \begin{cases} 150 \eta_{0.02}^{0.21}T_{\rm
C,9}^{0.21}\epsilon_{-2}^{0.21} M_{\bullet,8}^{0.16}\,{\rm km\,s^{-1}}
&, \text{core}\\ 130 \eta_{0.02}^{0.29}T_{\rm
C,9}^{0.29}\epsilon_{-2}^{0.29} M_{\bullet,8}^{0.14}\,{\rm km\,s^{-1}}
&, \text{cusp},
  \end{cases}
  \label{eq:vC2}
\end{align}

@@

The total gas heating rate, $\vwO$, includes contributions from
stellar winds, supernovae, pulsars, and SMBH feedback.  The strength
of each heating source will depend explicitely on the SMBH mass and
the star formation hstory in the galactic nuclear region, the latter
of which will also vary systematically with the galaxy mass and hence
with $\Mbh$.

Figure~\ref{fig:vwSourcesImp} shows the contributions of various heating sources as a
function of time $\tau_{\star}$ after a burst of star formation for a
black hole masses of $\Mbh = 10^{6} \Msun$.  These heating
rates are calculated using the stellar wind heating $v_{\rm
  w}^{\star}$ (Fig.~\ref{fig:vwImp}) and mass return parameter $\eta$
(Fig.~\ref{fig:eta}), the latter of which affects the other sources of
feedback, including AGN ($v_{\rm w}^{\bullet}$; eqs.~[\ref{eq:vC}],
[\ref{eq:vjet}]), millisecond pulsars ($v_{w}^{\rm msp}$;
eq.~[\ref{eq:vmsp}]), and Ia supernovae ($v_{w}^{\rm Ia}$;
eq.~[\ref{eq:vIa}]).  The Ia heating rate also depends on a
convolution of the star formation history and the Ia delay-time
distribution (eq.~[\ref{eq:DTD}]).  At very early times ($\tau_{\star}
\lesssim XXX$), stellar wind heating dominates, but at later times
Compton heating dominates.  MSP heating is again found to be
negligible at all black hole masses.  Epochs of thermally-unstable
accretion are shown as a dashed line, indicating that Compton heating
becomes important only during the phase of unstable accretion.

From Figure~\ref{fig:vwSourcesImp} we conclude that thermally unstable accretion is the
norm.  However, a single burst of star formation does not describe the
average star formation histories of most galaxies.  Qualitatively,
smaller galaxies will on average have more recent star formation,
resulting in energetic young stellar winds and supernovae which
dominate the energy budget, resulting in a high heating rate of $\vwO
\sim 1000 $ km s$^{-1}$.  Massive galaxies, on the other hand, will on
average have older stellar populations, with their heating rates
dominated by Ia supernovae (on large radial scales) and SMBH feedback.
The average value of $\vwO$ is estimated as a function of SMBH mass
for each heating source by calculating its value using the average
cosmic star formation histories of \citet{MosterNaab+:2013a}.
Appendix \ref{app:windheat} describes how the average star formation
history is used to determine the stellar wind heating $v_{\rm
  w}^{\star}$ and mass return parameter $\eta$ (Fig.~\ref{fig:eta}).

@@

\begin{figure}
\includegraphics[width=\columnwidth]{vwSourcesImp.pdf}
\caption{\label{fig:vwSourcesImp} Blah Blah}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{eta.pdf}
\caption{\label{fig:eta} Parameter $\eta$ characterizing stellar mass
  loss rate (eq.~[\ref{eq:q}]) as a function of black hole mass
  $\Mbh$, calculated for average star formation histories from
  \citet{MosterNaab+:2013a}  Note that the star
  formation histories in \citet{MosterNaab+:2013a} are in terms of
  halo mass and for each $\Mbh$ we assign the halo mass,
  whose star formation history would produce a bulge consistent with
  the $\Mbh-M_{\rm bulge}$ relationship from
  \citet{McConnellMa:2013a}.}
\end{figure}

@@

Figure~\ref{fig:miller} shows our predicted ${\rm L_{X}/L_{edd}}$ for
core (blue) and cusp (green) galaxies superimposed with x-ray
measurements (red stars), upper limits (red triangles) from
\citet{Miller+15}.  For our theoretical predictions $L_X=\epsilon
\Mdot c^2$, where $\epsilon$ is and efficiency factor and $\Mdot$ is
calculated using Equation~\eqref{eq:mdot_analytic}, with the value of
the wind heating parameter, $\vw$, and the mass return parameter,
$\eta$ set by the average star formation history for each $\Mbh$ (see
the black lines in Figures~\ref{fig:vwSource} and~\ref{fig:eta}). We
try two different prescriptions for $\epsilon$: 
$\epsilon=10^{-4}$ in the left-hand panel and $\epsilon=10^{-1}
\Mdot/0.01 \MdotEdd$ right-hand panel.

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{edd}$ predicted
  from our models compared to $L_X/L_{Edd}$ values (red stars) and
  upper limits (red triangles) from \citet{Miller+15}.
  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
  blue curves represent our predictions for core ($\Gamma=0.1$, blue)
  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
  from equation~\eqref{eq:mdot_analytic}. The wind heating
  parameter, $v_w$ and mass return parameter, $\eta$, calculated for
  the average star formation histories in \citet{MosterNaab+:2013a}
  (the black lines in Figures~\ref{fig:vwSources}
  and~\ref{fig:eta}). Note that the star formation histories in
  \citet{MosterNaab+:2013a} are in terms of halo mass and for each
  $\Mbh$ we assign the halo mass, whose star formation history would
  produce a bulge consistent with the $\Mbh-M_{\rm bulge}$
  relationship from \citet{McConnellMa:2013a}.  We also show upper
  limits $\epsilon_X \Mdot c^2/L_{edd}$ from thermal stability
  (purple) and Ia supernovae (orange).}
\end{figure*}

% Hower, the mass accretion rate is also a sensitive function of the assumed heating rate, such that $\dot{M}\sim\vwO^{-3.8(-2.4)}$ for a core(cusp) galaxies, respectively.  Thus, only a weak positive dependence of $v_{w} \propto M_{\bullet}^{0.25-0.3}$ would be sufficient to explain the trend in X-ray luminosity with BH masses in scenarios where $L_X \propto \dot{M}$, or a somewhat steeper dependence $v_{w} \propto M_{\bullet}^{0.35-0.45}$ if $L_{X} \propto \dot{M}^{2}$.  What could cause this dependence?  Maybe Ia SNa...

@@

% One possible solution that the wind mass loss rate $\eta$ increases
% with $\Mbh$, as would be expected if low mass SMBH preferentially
% hosted younger stellar populations.  Another possible explanation is
% that the effective heating rate of the CNM $v_{w}$ decreases
% with decreasing SMBH mass.  This could again be due to an older
% stellar population, since $v_{w} \propto \eta^{-1/2}$ for heating
% sources such as SN Ia and millisecond pulsars.
% {\bf AG given our new results on stellar wind heating as a function of
% Mbh. It seems like the first statement is indeed true but I suspect
% vwO actually increases for low Mbh and that this effect actually dominates.}
%, or it could be due to the fact that Ia occur too infrequently inside
%the stagnation radius for low mass black holes.
%AG-We now think that SNe Ia would become important only at the
%highest values of Mbh.
%AG-Note sure where the best place for this discussion would
%be--here or after presenting the comparisons with Miller et al.
